---
title: "p8105_hw1_al3998"
author: "AimingLiu"
date: "9/15/2019"
output: github_document
---
# Problem 1

This is the first code chunk for Problem 1

```{r}
library(tidyverse)

pr_df=tibble(
   ra_sample = rnorm(8),
    gr_th_0 = ra_sample>0,
    var_char = c("This","is","my","eight","characters","in","problem","one"),
    var_fac = factor(c("child","adult","elder","adult","elder","adult","child","adult"),levels=c("child","adult","elder"))
)
```
#Take the mean
The variable ra_sample has a mean of `r mean(pull(pr_df,ra_sample))`,and the variable gr_th_0 has a mean of `r mean(pull(pr_df,gr_th_0))`.
The mean of variable `var_char` is `r mean(pull(pr_df,var_char))`,the mean of variable `var_fac` is `r mean(pull(pr_df,var_fac))`

```{r convert types,eval = FALSE}
as.numeric(pull(pr_df,gr_th_0))
as.numeric(pull(pr_df,var_char))
as.numeric(pull(pr_df,var_fac))
```

When converting logical values into numeric values,the logical value `True` takes the numeric value `1` and `False` takes the numeric value `0`.When calculating the mean of logical values,R converts them to `1` and `0`.

When converting character value into numeric ones,the character variables in this data frame are consisted of letters which may lead to `NA` when converting them to numeric value.Then,when we take the mean of them,the result will be `NA`.

When converting factor values into numeric ones,the different levels may be converted into `1`,`2` and `3`.And here,when we take the mean,it also shows`NA` because that this assignment of value is not universal.

Here is the second chunk in problem 1.
```{r}
#convert the logical vector to numeric, and multiply the random sample by the result#
gr_th_0_num = as.numeric(pull(pr_df,gr_th_0))
(gr_th_0_num)*(pull(pr_df,ra_sample))

#convert the logical vector to a factor, and multiply the random sample by the result#
gr_th_0_fac = as.factor(pull(pr_df,gr_th_0))
(gr_th_0_fac)*(pull(pr_df,ra_sample))

#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result#
gr_th_0_facnum = as.numeric(gr_th_0_fac)
(gr_th_0_facnum)*(pull(pr_df,ra_sample))
```

# Problem 2
This is the code chunk for problem 2
```{r}
pr2_df=tibble(
  x = rnorm(500),
  y = rnorm(500),
  gr_th_1 = x+y>1,
  gr_th_1_num = as.numeric(gr_th_1),
  gr_th_1_fac = as.factor(gr_th_1)
)
```
The size of the data set can be described through the row and column of it.The column of the data set is `r ncol(pr2_df)` and the row of the data set is `r nrow(pr2_df)`.

The mean of x can be described as `r mean(pull(pr2_df,x))`.
The median of x can be described as `r median(pull(pr2_df,x))`.
The standard deviation of x can be described as `r sd(pull(pr2_df,x))`.

The proportion of cases for which x+y>1 can be described as `r sum(pull(pr2_df,gr_th_1))/length(pull(pr2_df,gr_th_1))`.

### The scatterplot of y vs x
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1))
```

### The scatterplot of numeric variables
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1_num))
```

### The scatterplot of factor variables
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1_fac))
```

```{r}
logical_plot=ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1))
ggsave("scatterplot1.pdf",logical_plot,height = 8,width = 5)
```
