---
title: "p8105_hw1_al3998"
author: "AimingLiu"
date: "9/14/2019"
output: github_document
---
# Problem 1

This is the first code chunk for Problem 1

```{r}
library(tidyverse)

pr_df=tibble(
   ra_sample = rnorm(8),
    gr_th_0 = ra_sample>0,
    var_char = c("This","is","my","eight","characters","in","problem","one"),
    var_fac = factor(c("child","adult","elder","adult","elder","adult","child","adult"),levels=c("child","adult","elder"))
)
```

Here is the second chunk in problem 1.
```{r}
#convert the logical vector to numeric, and multiply the random sample by the result#
gr_th_0_num = as.numeric(pr_df$gr_th_0)
(gr_th_0_num)*(pr_df$ra_sample)

#convert the logical vector to a factor, and multiply the random sample by the result#
gr_th_0_fac = as.factor(pr_df$gr_th_0)
(gr_th_0_fac)*(pr_df$ra_sample)

#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result#
gr_th_0_facnum = as.numeric(gr_th_0_fac)
(gr_th_0_facnum)*(pr_df$ra_sample)
```

# Problem 2
This is the code chunk for problem 2
```{r}
pr2_df=tibble(
  x = rnorm(500),
  y = rnorm(500),
  gr_th_1 = x+y>1,
  gr_th_1_num = as.numeric(gr_th_1),
  gr_th_1_fac = as.factor(gr_th_1)
)
```
The size of the data set can be described through the row and column of it.The column of the data set is `r ncol(pr2_df)` and the row of the data set is `r nrow(pr2_df)`.

The mean of x can be described as `r mean(pr2_df$x)`.
The median of x can be described as `r median(pr2_df$x)`.
The standard deviation of x can be described as `r sd(pr2_df$x)`.

The proportion of cases for which x+y>1 can be described as `r sum(pr2_df$gr_th_1)/length(pr2_df$gr_th_1)`.

### The scatterplot of y vs x
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1))
```

### The scatterplot of numeric variables
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1_num))
```

### The scatterplot of factor variables
```{r}
ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1_fac))
```

```{r}
logical_plot=ggplot(pr2_df,aes(x=x,y=y))+geom_point(aes(color=gr_th_1))
ggsave("scatterplot1.pdf",logical_plot,height = 8,width = 5)
```
